\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newcommand{\RR}{\mathbb{R}}
\DeclareMathOperator{\conv}{conv}

\title{Two hidden layers compute the maximum of six numbers}
\author{Matthew Sun}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
We prove that $\max(x_1,\dots,x_6)$ is exactly computable by a ReLU neural network with two hidden
layers of arbitrary width. This resolves an open problem of Bakaev, Brunck, Hertrich, Stade, and
Yehudayoff, who established the five-input case and explicitly left the six-input case open, and which is
also listed as open in subsequent work. We give an explicit construction as a signed combination of six
$S_6$-orbits of $P_2$ support functions with denominator $360$, together with an exact, floating-point
free computer-assisted proof of correctness. We show that such a representation must use cancellation --- a
signed Minkowski identity in which the simplex appears only after cancellation --- for all $n\ge 5$. We then
give computational evidence that six is the exact threshold: $\max_7$ and $\max_8$ are not representable in
the same family even after enlarging it. Finally we isolate the obstruction to a separation as a global,
cross-chamber phenomenon by a single-chamber invisibility lemma, and reduce a genuine two-versus-three
hidden-layer separation to a single lattice normal-form conjecture.
\end{abstract}

\section{Introduction}

A feedforward ReLU network with $k$ hidden layers computes a continuous piecewise-linear (CPWL) function,
and conversely every CPWL function arises this way~\cite{ABMM}. A central question is how the number of
hidden layers limits expressivity, and the canonical test function is the maximum
$\max_n(x)=\max(x_1,\dots,x_n)$. A balanced binary tree of pairwise maxima computes $\max_n$ with
$\lceil\log_2 n\rceil$ hidden layers, and Hertrich, Basu, Di~Summa, and Skutella~\cite{HBDS} conjectured
this is optimal: that exactly representing $\max_n$ requires $\lceil\log_2(n+1)\rceil$ hidden layers, which
would make the ReLU depth hierarchy strict.

The conjecture holds for integer weights: Haase, Hertrich, and Loho~\cite{HHL} proved an integer-weight
lower bound of $\lceil\log_2 n\rceil$ hidden layers via lattice-polytope volumes. Over the rationals the
picture differs. Bakaev, Brunck, Hertrich, Stade, and Yehudayoff~\cite{BBHSY} showed that $\max_5$ needs
only two hidden layers, disproving the $n=5$ case and improving the general upper bound, and they left
open whether two hidden layers suffice for six inputs.

\begin{theorem}\label{thm:main}
$\max(x_1,\dots,x_6)$ is computable by a ReLU network with two hidden layers.
\end{theorem}

The construction uses rational weights, as it must: the integer-weight lower bound~\cite{HHL} would
otherwise force three layers. Our proof is computer-assisted but exact; every arithmetic step is over the
integers or rationals, and no floating-point computation enters the certificate.

\section{Preliminaries}

For a polytope $P\subset\RR^n$ its support function is $h_P(x)=\max_{g\in P}\langle g,x\rangle$. Then
$\max_n=h_\Delta$ for the standard simplex $\Delta=\conv\{e_1,\dots,e_n\}$. Support functions are additive
under Minkowski sum, $h_{P+Q}=h_P+h_Q$, and satisfy $h_{\conv(A\cup B)}=\max(h_A,h_B)$; two polytopes with
equal support functions are equal.

Following~\cite{BBHSY}, define $P_0=\{\text{points}\}$ and
$P_{k+1}=\{\sum_i P_i * Q_i : P_i,Q_i\in P_k\}$, where $*$ is join (convex hull of union) and the sum is
Minkowski. Then $P_1$ is the class of zonotopes, and $P_2$ is Minkowski sums of \emph{joins of two
zonotopes}. A \emph{block} is $R=\conv(Z_1\cup Z_2)$ with $Z_1,Z_2$ zonotopes, and
$h_R(x)=\max\big(h_{Z_1}(x),h_{Z_2}(x)\big)$.

\begin{lemma}[Two-layer dictionary]\label{lem:dict}
A CPWL function $f:\RR^n\to\RR$ is computable by a ReLU network with two hidden layers if and only if
$f=\sum_{t} c_t\,h_{R_t}+\ell$ for finitely many blocks $R_t$, real coefficients $c_t$, and an affine-linear
$\ell$. In particular $\max_6\in$ two hidden layers iff $h_\Delta=\sum_t c_t h_{R_t}+\ell$ for blocks $R_t$.
\end{lemma}

\begin{proof}
By~\cite{ABMM,HHL} a function is $k$-hidden-layer computable iff it is a difference $h_Q-h_P$ of support
functions of $P,Q\in P_k$ (virtual polytopes), up to an affine term. For $k=2$, $P$ and $Q$ are Minkowski
sums of blocks, so by additivity $h_P=\sum_i h_{A_i}$ and $h_Q=\sum_j h_{B_j}$ over blocks $A_i,B_j$; then
$f=h_Q-h_P+\ell=\sum_j h_{B_j}-\sum_i h_{A_i}+\ell$ is a signed sum of block support functions. Conversely
any signed sum $\sum_t c_t h_{R_t}$ is $h_Q-h_P$ with $Q=\sum_{c_t>0}c_t R_t$ and $P=\sum_{c_t<0}(-c_t)R_t$
in $P_2$, hence two-hidden-layer. The affine $\ell$ is realized in the output layer.
\end{proof}

\paragraph{The weight-2 lattice.} We take building-block vertices on the weight-2 lattice points of the
dilated simplex $2\Delta^{5}$, namely $\{2e_i\}$ and $\{e_i+e_j\}$ (21 points in $\RR^6$); zonotopes are
generated by braid directions $e_a-e_b$ restricted so that all vertices stay on the lattice. This is the
lattice underlying the construction of~\cite{BBHSY} for $\max_5$. Write $V_2^{(2)}$ for the (finite) family
of signed sums of block support functions with all block vertices in this lattice.

\begin{lemma}[Symmetrization]\label{lem:sym}
If $h_\Delta=\sum_t c_t h_{R_t}+\ell$ with blocks $R_t$, then also
$h_\Delta=\sum_t c_t\big(\tfrac{1}{|S_n|}\sum_{\sigma\in S_n} h_{\sigma R_t}\big)+\bar\ell$, an
$S_n$-symmetric representation in which each term is an orbit sum of blocks and $\bar\ell$ is the symmetric
linear function $\tfrac{1}{n}(\sum_i x_i)\cdot(\text{const})$. Consequently $\max_n\in$ two layers iff it has
an $S_n$-symmetric such representation, and the search may be restricted to $S_n$-orbits of blocks (for
$n=6$ this collapses $16390$ two-way joins to $78$ orbit classes, making an exact linear solve tractable).
\end{lemma}

\begin{proof}
For $\sigma\in S_n$, $h_{\sigma R}(x)=h_R(\sigma^{-1}x)$, and $h_\Delta$ is $S_n$-invariant
($h_\Delta(\sigma^{-1}x)=h_\Delta(x)$, since $\sigma$ permutes the vertices of $\Delta$). Averaging the
identity $h_\Delta=\sum_t c_t h_{R_t}+\ell$ over $\sigma\in S_n$ gives $h_\Delta=\sum_t c_t\,
\overline{h_{R_t}}+\bar\ell$, where $\overline{h_{R_t}}=\tfrac1{|S_n|}\sum_\sigma h_{\sigma R_t}$. Each
$\sigma R_t$ is again a block ($\sigma$ maps zonotopes to zonotopes), so $\overline{h_{R_t}}$ is a
nonnegative combination of block support functions and the whole representation remains a signed sum of
block support functions (Lemma~\ref{lem:dict}); equivalently $\overline{h_{R_t}}=\tfrac1{|S_n|}
h_{\sum_\sigma\sigma R_t}$ is a positive multiple of the support function of the $S_n$-symmetric Minkowski
orbit sum $\sum_\sigma\sigma R_t$. For the linear part, write $\ell(x)=\langle a,x\rangle+b$; then
$\bar\ell(x)=\langle\bar a,x\rangle+b$ with $\bar a=\tfrac1{|S_n|}\sum_\sigma\sigma a=\tfrac1n(\sum_i a_i)
\mathbf 1$, so $\bar\ell$ is a multiple of $\sum_i x_i$ plus the constant $b$. Evaluating the original
identity at $x=0$ gives $b=0$ (support functions vanish at the origin), so $\bar\ell$ is a scalar multiple
of $\sum_i x_i$.
\end{proof}

\section{The construction}

Solving exactly for orbit coefficients reproducing $\max_6$ and minimizing the number of terms yields a
construction with six orbit terms and denominator $D=360$:
\[
   \max_6 = \sum_{o=1}^{6} c_o \Big(\sum_{R\in o} h_R\Big), \qquad
   c_o \in \Big\{ \tfrac{1}{360}, -\tfrac{1}{360}, \tfrac{1}{360}, \tfrac{1}{90}, -\tfrac{1}{90}, -\tfrac{1}{180} \Big\},
\]
with zero linear part. The six orbit representatives, as vertex (gradient) sets, are listed in the
accompanying file \texttt{construction\_max6.txt}. Each $R$ is a join of two weight-2 zonotopes, so each
$h_R$ is a two-hidden-layer function and the signed sum is two hidden layers. Expanding the six orbits
over $S_6$ gives $1530$ individual $P_2$ terms.

The construction uses negative coefficients, and this is unavoidable: the representation is a genuine
\emph{virtual} (signed) Minkowski identity in which the simplex appears only after cancellation.

\begin{proposition}[Necessity of cancellation]\label{prop:neg}
For $n\ge 5$, every representation of $\max_n$ as a signed sum $\sum_t c_t h_{R_t}+\ell$ of support
functions of two-way joins of zonotopes (with $\ell$ linear) has at least one negative coefficient.
\end{proposition}

\begin{proof}
Suppose all $c_t\ge 0$. Write $\ell(x)=\langle a,x\rangle+b$; evaluating the identity
$h_\Delta=\sum_t c_t h_{R_t}+\ell$ at $x=0$ forces $b=0$ (support functions vanish at the origin), so
$\ell=h_{\{a\}}$ and additivity gives $h_\Delta=h_{\,a+\sum_t c_t R_t}$, whence $\Delta=a+\sum_t c_t R_t$ as
a Minkowski sum. For each $t$, grouping the identity as $\Delta=(c_t R_t)+\big(a+\sum_{s\ne t}c_s R_s\big)$
exhibits $c_t R_t$ as a Minkowski summand of $\Delta$; since a simplex of dimension $\ge 2$ is Minkowski
indecomposable up to homothety and translation (Shephard; McMullen), each nonzero $c_t R_t$ is homothetic
to $\Delta$, i.e.\ each nonzero $R_t$ is a homothet of $\Delta$.

It remains to show that a homothet of the $(n-1)$-simplex is a two-way join of zonotopes only for
$n\le 4$. Let $S=\conv(Z_1\cup Z_2)$ be an $(n-1)$-simplex with $Z_1,Z_2$ zonotopes. Each $Z_i$ is centrally
symmetric about some center $c_i$. If a vertex $v$ of $S$ is a vertex of $Z_i$, then by central symmetry
$2c_i-v\in Z_i\subseteq S$; in barycentric coordinates on $S$ with $v=e_j$, membership $2c_i-v\in S$ forces
the $j$-th barycentric coordinate to be nonnegative, i.e.\ $2(c_i)_j-1\ge 0$, so $(c_i)_j\ge\tfrac12$.
Hence at most two vertices of $S$ can be vertices of $Z_i$: three would give three barycentric coordinates
of $c_i$ each $\ge\tfrac12$, summing to more than $1$, impossible. Now every vertex of $S$ is an extreme
point of $Z_1\cup Z_2$, hence a vertex of $Z_1$ or of $Z_2$; so $S$ has at most $2+2=4$ vertices, i.e.\
$n\le 4$, contradicting $n\ge 5$. (The bound is sharp: for $n=4$ a tetrahedron is the join of two skew
segments.)
\end{proof}

For $n=4$ a single term (no negativity) suffices; $\max_5$ and $\max_6$ require cancellation. This is why
single-polytope invariants (central symmetry, volume) do not obstruct: the obstruction lives in the
cancellation, not in any individual body.

\section{The proof of Theorem~\ref{thm:main}}

Let $C=\sum_{o} c_o\big(\sum_{R\in o}h_R\big)$ denote the construction of the previous section, a CPWL
function. We must show $C=h_\Delta=\max_6$ on all of $\RR^6$. We proceed by three lemmas and two
machine-checked computational facts; every step below is exact (integer or rational), with no
floating-point arithmetic.

\begin{lemma}[Gradient reduction]\label{lem:grad}
$C$ and $\max_6$ are CPWL. If $\nabla C=e_1$ at an interior point of every full-dimensional cell of the
weight-2 difference arrangement inside the open fundamental cone $\{x_1>\cdots>x_6\}$, then $C=\max_6$ on
all of $\RR^6$.
\end{lemma}

\begin{proof}
On any region where no block changes its maximizing vertex, $\nabla C=\sum_t c_t\,g_t^\ast$ with
$g_t^\ast=\arg\max_{g\in R_t}\langle g,x\rangle$; the selection $g_t^\ast$ is locally constant and changes
only across the hyperplanes $\langle g-g',x\rangle=0$ for $g,g'$ vertices of a common block (the weight-2
difference hyperplanes), so these hyperplanes contain all non-smooth loci of $C$. Inside a cell every
relevant comparison is strict, so each $g_t^\ast$ is unique and $\nabla C$ is well defined and constant.
On the open fundamental cone $\max_6=x_1$ so $\nabla\max_6=e_1$. Suppose $\nabla C=e_1$ at an interior
point of every cell. Since $C$ is affine on each cell, $\nabla C=e_1$ throughout each open cell, so $C-x_1$
is constant on each cell; by continuity of the CPWL function $C-x_1$ across a shared wall, the constants on
two adjacent cells agree, and since the cell-adjacency graph of the arrangement inside the connected open
cone is connected (Lemma~\ref{lem:closure}), $C-x_1$ equals a single constant $\kappa$ on the open cone,
hence on its closure. As $C$ and $x_1$ are positively homogeneous of degree $1$, so is $C-x_1$; thus
$\kappa=(C-x_1)(\lambda x)=\lambda\kappa$ for all $\lambda>0$, forcing $\kappa=0$. Therefore $C=x_1=\max_6$
on the closed fundamental chamber. Both $C$ (an orbit-summed signed sum) and $\max_6$ are $S_6$-invariant,
and $S_6\cdot\{x_1\ge\cdots\ge x_6\}=\RR^6$, so equality on one chamber gives equality on all of $\RR^6$.
\end{proof}

\begin{lemma}[Forced directions]\label{lem:forced}
In gap coordinates $y_k=x_k-x_{k+1}\ge 0$ ($k=1,\dots,5$), a difference hyperplane with normal $h$ becomes
$\sum_k\big(\sum_{i\le k}h_i\big)y_k=0$. If all coefficients $\sum_{i\le k}h_i$ have one sign, the
hyperplane meets the open cone $y>0$ trivially and cannot subdivide it. Of the $120$ distinct weight-2
difference hyperplanes, exactly $85$ are so forced; the cell structure inside $y>0$ is therefore the
arrangement of the remaining $35$ hyperplanes in $\RR^5$.
\end{lemma}

\begin{proof}
The change of coordinates $x\mapsto y$ is linear with $x_i-x_j=\sum_{i\le k<j}y_k$; substituting gives the
stated form. If every prefix sum $\sum_{i\le k}h_i$ is $\ge 0$ (resp.\ $\le 0$), the linear form is
$\ge 0$ (resp.\ $\le 0$) on $y\ge 0$ and vanishes on $y>0$ nowhere, so the hyperplane does not cut the open
cone. Counting the forced normals among the $120$ difference directions leaves $35$ unforced; only these
subdivide $\{y>0\}$. (The counts $85$ and $35$ are verified by exact integer arithmetic in
\texttt{check\_max6.py}.)
\end{proof}

\paragraph{Computational Fact 1 (enumeration).} A deterministic depth-first search over sign vectors of the
$35$ unforced normals, pruning branches whose open sign system is infeasible, enumerates exactly $2608$
full-dimensional cells of $\{y>0\}$, each with an explicit exact integer interior witness.

\paragraph{Computational Fact 2 (gradient).} At each of the $2608$ integer witnesses, the exact-integer
gradient $\sum_t c_t\,g_t^\ast=e_1$.

Both facts are established by exact integer computation in \texttt{check\_max6.py}. As an independent
check, evaluating $C$ and $\max_6$ in exact rational arithmetic at random points --- including boundary and
tie configurations --- confirms $C=\max_6$ with zero error. It remains only to certify that the enumeration
is complete.

\begin{lemma}[Completeness by adjacency closure]\label{lem:closure}
Let $\mathcal{C}$ be the set of $2608$ enumerated cells. If for every cell in $\mathcal{C}$ and every
single-coordinate sign flip the resulting open sign system is either another cell of $\mathcal{C}$ or
certifiably empty, then $\mathcal{C}$ is the set of all full-dimensional cells of the arrangement inside
$\{y>0\}$.
\end{lemma}

\begin{proof}
The full-dimensional cells of a hyperplane arrangement inside the connected open cone $\{y>0\}$ form the
vertices of a graph in which two cells are adjacent iff their (closed) sign vectors differ in exactly one
coordinate; this graph is connected (any two points of the cone are joined by a path crossing one wall at a
time). $\mathcal{C}$ is nonempty and, by hypothesis, closed under adjacency (each neighbor is in
$\mathcal{C}$ or empty, i.e.\ not a cell). A nonempty subset of a connected graph closed under adjacency is
the whole vertex set, so $\mathcal{C}$ contains every cell. Emptiness of a flipped sign system
$\{y:\langle g_j,y\rangle>0\ \forall j\}$ is certified exactly by Gordan's theorem: the open system is
infeasible iff there exist nonnegative rationals $x_j$, not all zero, with $\sum_j x_j g_j=0$ (over the
orthant generators and the signed normals); such an $x$ is exhibited and the identity checked over
$\mathbb{Q}$. Across all $2608\times 35$ flips every neighbor is in-set ($13756$) or Gordan-certified empty
($77524$), none uncertified.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
By Lemma~\ref{lem:forced} the cells of the fundamental cone are those of the $35$-hyperplane arrangement.
By Computational Fact~1 and Lemma~\ref{lem:closure} the $2608$ enumerated cells are \emph{all} of them.
By Computational Fact~2, $\nabla C=e_1$ at an interior witness of each. By Lemma~\ref{lem:grad}, $C=\max_6$
on $\RR^6$. Since $C$ is a signed sum of block support functions, Lemma~\ref{lem:dict} makes it a
two-hidden-layer ReLU function. \qed
\end{proof}

\section{The threshold and a route to a separation}

The two-hidden-layer functions whose building blocks have vertices in the weight-2 lattice form a finite
family: a weight-2 zonotope has vertices among the finitely many lattice points, and the building blocks
are the two-way joins of such zonotopes (including degenerate point zonotopes, giving pyramids). We
enumerate this family completely (all zonotopes generated by arbitrary, not merely braid, weight-2 point
differences) and solve over $\mathbb{Q}$.

\begin{proposition}\label{prop:max7}
$\max_7$ is not a signed sum of support functions of two-way joins of weight-2 zonotopes. Equivalently,
$\max_7$ has no two-hidden-layer representation with all building-block vertices in the weight-2 lattice.
\end{proposition}

This is exact: the complete family yields a linear system over $\mathbb{Q}$ that is inconsistent for
$\max_7$ (and consistent for $\max_6$, recovering Theorem~\ref{thm:main}). The same holds for $\max_8$.
This locates a qualitative change exactly at $n=6$, and we conjecture:

\begin{conjecture}
$\max_n$ is computable in two hidden layers if and only if $n\le 6$.
\end{conjecture}

Proposition~\ref{prop:max7} is a genuine lower bound over the weight-2 lattice; what is missing for an
unconditional separation is only that the lattice may be assumed weight-2. The reduction $\max_n$ two-layer $\iff \Delta+P=Q$ with $P,Q\in P_2$ is standard; one checks
that any representation may be symmetrized, and that $\Delta+P=Q$ forces the normal fan of $Q$ to refine
the braid fan. The remaining content is a normal-form lemma:

\begin{conjecture}[Lattice normal form]
If $\max_n$ is computable in two hidden layers, it has a representation with all building-block vertices in
the weight-2 lattice.
\end{conjecture}

Granting this, two-layer representability becomes a finite computation, and the $n=7$ negative becomes the
statement that $\max_7$ requires three hidden layers, a separation of two from three hidden layers over the
reals.

The difficulty of the normal-form lemma has a clean structural source: the obstruction is invisible inside
any single chamber of the braid arrangement. Let $D=\{x_1\ge\cdots\ge x_n\}$ be the closed fundamental
chamber; on $D$ one has $\max_n=x_1$, a linear function.

\begin{lemma}[Single-chamber invisibility]\label{lem:chamber}
Let $\lambda$ be a finite signed combination of point evaluations, all at points of a single open braid
chamber, and suppose $\lambda$ annihilates every linear function. Then $\lambda(\max_n)=0$. Consequently,
any separating functional --- one with $\lambda(h_R)=0$ for all blocks $R$, $\lambda(\ell)=0$ for all
linear $\ell$, and $\lambda(\max_n)\ne 0$ --- cannot have all its evaluation points in a single open braid
chamber; it must draw on at least two chambers.
\end{lemma}

\begin{proof}
On one open braid chamber $\{x_{\sigma(1)}>\cdots>x_{\sigma(n)}\}$, the largest coordinate is
$x_{\sigma(1)}$ at every point (the ordering index $\sigma$ is constant on the chamber), so $\max_n$ agrees
there with the single linear function $\ell^\ast(x)=x_{\sigma(1)}$. Since all evaluation points lie in that
chamber and $\lambda$ annihilates linear functions,
$\lambda(\max_n)=\sum_r a_r\max_n(z_r)=\sum_r a_r\ell^\ast(z_r)=\lambda(\ell^\ast)=0$. The second statement
is the contrapositive: if $\lambda(\max_n)\ne 0$, its evaluation points cannot all lie in one open chamber.
\end{proof}

Thus the membership obstruction is a genuinely global, cross-chamber compatibility failure: the local
linear pieces of $\max_n$ exist chamber by chamber but need not glue to a symmetric $P_2$ representation.
This is borne out at the level of certificates: the exact rational functional witnessing
Proposition~\ref{prop:max7} at weight~$2$ has minimal support $\operatorname{rank}+1$ spread across almost
as many distinct braid chambers, with no sparse or single-chamber representative, exactly as
Lemma~\ref{lem:chamber} predicts. It also explains why single-chamber or local-linear tests (and, in our
experiments, low-order finite differences, wall relaxations, and mixed-volume comparisons) do not
obstruct: they cannot see a cross-chamber phenomenon. (We caution that the Lemma rules out single-chamber
certificates only; adjacent-chamber and higher-order tests can still detect finite-family obstructions.)

The route this suggests is a global one. We note first that the conformity route is closed: the optimal
shallow construction is provably not braid-conforming (indeed our $\max_6$ construction requires
non-conforming blocks), consistent with the conditional bounds of Grillo, Hertrich, and Loho~\cite{GHL}.
The relevant tools for the lattice normal form are the decomposition polyhedra of Brandenburg, Grillo, and
Hertrich~\cite{BGH} --- the natural global object, in which two-layer representations are extreme
decompositions and non-representability is emptiness of the $P_2$-restricted polyhedron --- and
deformation-cone theory for the braid fan. Contemporary lower bounds are consistent with
Theorem~\ref{thm:main}: \cite{HHL} is integer-weight only, \cite{AHM} is for finite-precision weights,
\cite{GHL} is for braid-conforming networks, and \cite{Saf} is a width rather than depth bound at depth at
least three.

\begin{thebibliography}{9}
\bibitem{ABMM} R.~Arora, A.~Basu, P.~Mianjy, A.~Mukherjee. Understanding Deep Neural Networks with
Rectified Linear Units. ICLR 2018. arXiv:1611.01491.
\bibitem{HBDS} C.~Hertrich, A.~Basu, M.~Di~Summa, M.~Skutella. Towards Lower Bounds on the Depth of ReLU
Neural Networks. NeurIPS 2021; SIAM J. Discrete Math. 37(2):997--1029, 2023. arXiv:2105.14835.
\bibitem{HHL} C.~Haase, C.~Hertrich, G.~Loho. Lower Bounds on the Depth of Integral ReLU Neural Networks
via Lattice Polytopes. ICLR 2023. arXiv:2302.12553.
\bibitem{BBHSY} E.~Bakaev, F.~Brunck, C.~Hertrich, J.~Stade, A.~Yehudayoff. Better Neural Network
Expressivity: Subdividing the Simplex. STOC 2026. arXiv:2505.14338.
\bibitem{BGH} M.~Brandenburg, M.~Grillo, C.~Hertrich. Decomposition Polyhedra of Piecewise Linear
Functions. ICLR 2025. arXiv:2410.04907.
\bibitem{GHL} M.~Grillo, C.~Hertrich, G.~Loho. Depth-Bounds for Neural Networks via the Braid Arrangement.
NeurIPS 2025. arXiv:2502.09324.
\bibitem{AHM} G.~Averkov, C.~Hojny, M.~Merkert. On the Expressiveness of Rational ReLU Neural Networks
With Bounded Depth. ICLR 2025. arXiv:2502.06283.
\bibitem{Saf} I.~Safran. A Depth Hierarchy for Computing the Maximum in ReLU Networks via Extremal Graph
Theory. 2026. arXiv:2601.01417.
\end{thebibliography}

\end{document}
